\documentclass[11pt,letterpaper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.85in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.25em}
\setlist[itemize]{leftmargin=1.2em, topsep=0.2em, itemsep=0.15em}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{0.2em}\titlerule]
\titlespacing*{\section}{0pt}{0.9em}{0.5em}

\newcommand{\entry}[4]{%
    \textbf{#1} \hfill #2\\
    \textit{#3}\\
    #4
    \vspace{0.6em}
}

\begin{document}

{\LARGE\textbf{Kacper Krasowski}}\\[0.4em]
\href{mailto:kacperkrasowski2000@gmail.com}{kacperkrasowski2000@gmail.com}
\textbar{} +48 530 732 802
\textbar{} \href{https://kacperkrasowski.github.io/}{kacperkrasowski.github.io}

\vspace{0.8em}
PhD student in Economics at \textbf{Collegio Carlo Alberto} and \textbf{Universitat Aut\`onoma de Barcelona}. Research interests include digital technologies, social media algorithms, and artificial intelligence.

\section*{Education}

\entry{Collegio Carlo Alberto \& Universitat Aut\`onoma de Barcelona}{Sep 2024--Present}{PhD in Economics}{}

\entry{Universitat Aut\`onoma de Barcelona}{Oct 2022--Jul 2024}{MRes in Economics, Erasmus Mundus Joint Master Degree (EMJMD)}{}

\entry{Warsaw School of Economics}{Oct 2019--Jul 2022}{B.A. in Economics}{Quantitative Methods in Economics and Information Systems.}

\section*{Work in Progress}

\begin{itemize}
    \item \textbf{GenAI and the Internet} (2026).
    \item \textbf{Social Media and Labor Market Outcomes: An Analysis of Facebook Effect on College Graduates' Earnings} (with Luca Marcian\`o) (2025).
    \item \textbf{Impact of Censorship in Social Media} (2024).
\end{itemize}

\section*{Professional Experience}

\entry{The Econometric Society}{Mar 2026--Present}{Replicator}{
\begin{itemize}
    \item Independently verify the reproducibility of submitted research by testing authors' data, code, and documentation.
\end{itemize}
}

\entry{Review of Economic Studies}{Sep 2025--Present}{Social Media Manager}{
\begin{itemize}
    \item Manage social media accounts and support the journal's digital communications.
    \item Build and maintain REStud Tour websites.
\end{itemize}
}

\entry{Shopee Pte. Ltd.}{Mar 2022--Sep 2022}{Data Analyst}{
\begin{itemize}
    \item Conducted web scraping in Python.
    \item Performed data analysis in Excel.
\end{itemize}
}

\section*{Teaching Experience}

\entry{Econometrics I}{2025}{TA, University of Turin}{}

\section*{Selected Presentation}

\entry{BSE PhD Jamboree, Barcelona}{2026}{Presenter}{}

\section*{Awards \& Fellowships}

\textbf{Social Innovation Award, Social Hackathon} \hfill 2024\\
\textbf{UAB IDEA PhD Track Fellowship, Barcelona School of Economics} \hfill 2023\\
\textbf{Polish Economic Knowledge Olympiad — Finalist} \hfill 2019\\

\section*{Skills \& Languages}

\textbf{Programming and software:} R, Python, Stata, MATLAB, C, HTML, SQL, Bash, \LaTeX, MS Office.\\
\textbf{Languages:} Polish (native), English (proficient), Spanish (intermediate), Italian (intermediate).

\section*{Additional Information}

\textbf{Activities:} Member of the School Political Economy Science Club (2019--2020); volunteer in the Noble Gift finals (2018, 2019).\\
\textbf{Interests:} Languages (currently studying Catalan and Italian), chess, martial arts, skateboarding.

\vfill
{\small I hereby consent to the processing of my personal data pursuant to the EU General Data Protection Regulation 679/2016.}

\end{document}